cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_crescent definition

>>>>

The `gen_crescent(n, p)` function generates a $p$-dimensional dataset of $n$ observations based on a $2\text{-}D$ crescent-shaped manifold with optional structured high-dimensional noise.

The first two dimensions define a crescent-shaped curve using a semi-circular arc. Let $\theta \in [\pi/6, 2\pi]$ be a sequence of $n$ evenly spaced angles.

The corresponding $2\text{-}D$ coordinates are defined by:

$$
X_1 = \cos(\theta),
$$
$$
X_2 = \sin(\theta).
$$

This forms a nonlinear curvilinear structure in the shape of a tilted crescent in the $X_1$-$X_2$ plane.

For $p > 2$, additional dimensions $X_3$ to $X_p$ are generated using `gen_wavydims1()`:

$$
X_j = s_j \cdot \theta + \varepsilon_j$,\text{ where }$\varepsilon_j \sim \mathcal{N}(0, 0.5^2)$,\text{ and }$s_j$\text{ is a random scale}.
$$

These noise dimensions are nonlinearly correlated with $\theta$, producing structured, wave-like variation that aligns with the progression along the crescent curve.
